Deep Probabilistic Models for Camera Geo-Calibration

### 2018-08-23 chapters/introduction/introduction.tex
fix a citation

Automatic feature engineering has drawn a lot of attention over the
past years. Compared to the manual feature engineering,
automatic feature engineering approaches allow to learn useful
features without strong expert knowledge about the data. Among these
approaches, deep neural networks are wildly accepted as
good tools to learn high-level image representations.  The most
commonly used approach for deep feature learning is full supervision,
which usually requires manual
annotations~\cite{yosinski2015transferable,zhou2016learning,wen2016discriminative}.
Unfortunately, such data is not always available for certain tasks.
In contrast, unlabeled data is often plentiful (\ie cellphone photos
in Instagram or Youtube videos).

>>>>

Automatic feature engineering has drawn a lot of attention over the
past years. Compared to the manual feature engineering,
automatic feature engineering approaches allow to learn useful
features without strong expert knowledge about the data. Among these
approaches, deep neural networks are wildly accepted as
good tools to learn high-level image representations.  The most
commonly used approach for deep feature learning is full supervision,
which usually requires manual
annotations~\cite{yosinski2014transferable,zhou2016learning,wen2016discriminative}.
Unfortunately, such data is not always available for certain tasks.
In contrast, unlabeled data is often plentiful (\ie cellphone photos
in Instagram or Youtube videos).
